### 2022-06-09 README.Rmd
Small changes + LICENSE change
Small changes in code and changed license from MIT to GPL2 since the package depend on INLA which is GPL2

# Bremla
This Repository contains the Bremla package for uncertainty quantification and synchronization for layer-counted proxy archives, including all the data/code to reproduce the results for

@@

## Example

```{r example}
This is a real data example which produces 5000 simulations from a synchronized time scale.
require(INLA)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")

age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
d18O = NGRIP_5cm$d18O
proxy=d18O
data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
formula = dy~-1+depth2

>>>>

# Bremla
This Repository contains the Bremla package for uncertainty quantification and synchronization for layer-counted proxy archives, including the data and code to reproduce the results for

@@

## Example
This is a real data example which produces 5000 simulations from a synchronized time scale.
```{r example, message=FALSE, warning=FALSE, include=FALSE}
require(INLA)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")

age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
proxy = NGRIP_5cm$d18O

data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
formula = dy~-1+depth2
